\thispagestyle{empty}

\noindent 
\textsf{\textbf{\Large Master Thesis Abstract}}

\medskip


\noindent
Slovak University of Technology in Bratislava\\
Faculty of Electrical Engineering and Information Technology

\bigskip
\noindent
\begin{tabular}{@{}l l}
Branch of Study: & Cybernetics \\
Study Programme: & Robotics and Cybernetics \\
Author: & Bc. Andrii Stoliar \\
Thesis Title: & Implementation Design of Selected Control Algorithms \\
Supervisor: & Ing. Marián Tárník, PhD. \\
Month, Year: & May, 2026 \\
\end{tabular}

\bigskip
\noindent
Keywords: control systems, laboratory dynamic system, system identification, numerical simulation, PI controller, operating point switching, gain scheduling, adaptive control, MRAC, gradient method, MATLAB/Simulink, Arduino UNO, C++, Siemens PLC, TIA Portal, experimental verification

\bigskip
\noindent
This diploma thesis deals with the design, implementation and experimental
verification of selected control algorithms for a laboratory thermal system.
The main objective of the thesis is to build a control system for a real laboratory
dynamic system and to create a custom software design on several implementation
platforms. The thesis applies methods from the fields of system identification,
numerical simulation and evaluation of control quality.

The first part describes the used laboratory system, its inputs, outputs and the
method of communication with individual platforms. Based on experimentally
measured data, system identification is performed, while the obtained model serves
as a basis for the design and simulation verification of the control algorithms.
Subsequently, three control approaches are designed and implemented: a PI
controller, PI control with operating point switching and MRAC adaptive control
based on the gradient method.

The individual algorithms are implemented in MATLAB/Simulink, in C++ on the
Arduino UNO platform and on the Siemens SIMATIC S7-1200 G2 industrial PLC
system. The experimental verification is focused on assessing the functionality of
the designed control systems when controlling a real device. The results of the
thesis show the practical possibilities of implementing the selected algorithms on
different platforms and at the same time point out the influence of measurement,
timing, signal processing and hardware properties on the resulting behaviour of the
control system.



\pagebreak